\begin{longtable}{@{}l p{13cm}@{}}
  \caption{Incorrectly answered Praxis Reading questions: gold answer vs.\ the model's prediction and reasoning.}\label{tab:praxis_errors} \\
  \toprule
  \endfirsthead
  \toprule
  \endhead
  \multicolumn{2}{@{}l}{\textbf{q051}} \\
  \textbf{Passage}   & Use the following passage to answer questions 50 through 53. \newline Gettysburg is the market town---or borough, accurately speaking---of an exclusively farming population, planted in one of the most productive sections of the Keystone State. It is the seat \newline of justice of the county. It has a seminary and college of the German Lutheran Church, which give a certain tone and cast to its social life. In \newline short, Gettysburg seems in all things so entirely devoted to the pursuits of peace, there is so little that is suggestive of war and bloodshed, even if time had not mostly effaced all traces of that gigantic struggle that, coming as we do with one absorbing idea in mind, we find it hard to reconcile the facts of history with the facts as we find them. \newline There is another side to Gettysburg---a picturesque, a captivating side. One looks around upon the landscape with simple admiration. One's highest praise comes from the \newline feeling of quiet satisfaction with which the harmony of nature reveals the harmony of God. You are among the subsiding swells that the South Mountain has sent rippling off to the east. So completely is the village hid away \newline among these green swells that neither spire nor steeple is seen until, upon turning one of the numerous low ridges by which the face of the country is so cut up, you enter a valley, not deep, but well defined by two opposite ranges \newline of heights, and Gettysburg lies gleaming in the declining sun before you---a picture to be long remembered. \newline Source: Excerpt from The Battle of Gettysburg 1863 by Samuel Adams Drake    \\
  \textbf{Question}  & 51. Which sentence from the passage contains both a fact and an opinion? \newline a. It is the seat of justice of the county. \newline b. In short, Gettysburg seems in all things so entirely devoted to the pursuits of peace, there is so little that is suggestive of war and bloodshed, even if time had not mostly effaced all traces of that gigantic struggle that, coming as we do with one absorbing idea in mind, we find it hard to reconcile the facts of history with the facts as we find them. \newline c. There is another side to Gettysburg---a picturesque, a captivating side. \newline d. One's highest praise comes from the feeling of quiet satisfaction with which the harmony of nature reveals the harmony of God. \newline e. So completely is the village hid away among these green swells that neither spire nor steeple is seen until, upon turning one of the numerous low ridges by which the face of the country is so cut up, you enter a valley, \newline not deep, but well defined by two opposite ranges of heights, and Gettysburg lies gleaming in the declining sun before you---a picture to be long remembered.   \\
  \textbf{Gold}      & E       \\
  \textbf{Model}     & B  \\
  \textbf{Reasoning} & \textit{--}  \\
  \midrule
  \multicolumn{2}{@{}l}{\textbf{q037}} \\
  \textbf{Passage}   & Use the following passage to answer questions 34 through 38. \newline The color of animals is by no means a matter of chance; it depends on many considerations, but in the majority of cases tends to protect the animal from danger by rendering it less conspicu- \newline ous. Perhaps it may be said that if coloring is mainly protective, there ought to be but few brightly colored animals. There are, however, not a few cases in which vivid colors are themselves protective. The kingfisher itself, though \newline so brightly colored, is by no means easy to see. The blue harmonizes with the water, and the bird as it darts along the stream looks almost like a flash of sunlight; besides which, protection is not the only consideration. Let us now \newline consider the prevalent colors of animals and see how far they support the rule. \newline Desert animals are generally the color of the desert. Thus, for instance, the lion, the antelope, and the wild ass are all sand-colored. \newline "Indeed," says Canon Tristram, "in the desert, where neither trees, brushwood, nor even undulation of the surface afford the slightest protection to its foes, a modification of color which shall be assimilated to that of the sur- \newline rounding country is absolutely necessary. Hence, without exception, the upper plumage of every bird, whether lark, chat, sylvain, or sand grouse, and also the fur of all the smaller mammals and the skin of all the snakes and \newline lizards, is of one uniform sand color." \newline Source: Excerpt from "The Colors of Animals" by Sir John Lubbock    \\
  \textbf{Question}  & 37. The author includes the quotation from Canon Tristram in order to \newline a. show that authorities agree with the author's opinions. \newline b. illustrate an idea that the author could not have explained himself. \newline c. support an argument that is not very popular. \newline d. prove that birds are unique creatures. \newline e. develop upon an idea the author had already introduced.   \\
  \textbf{Gold}      & E       \\
  \textbf{Model}     & A  \\
  \textbf{Reasoning} & \textit{--}  \\
  \midrule
  \bottomrule
\end{longtable}